VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_conc.tex
re

Our evaluation with an Alibaba dataset has the following results.
\begin{itemize}
\item {\em Competitive deduplication efficiency with a tradeoff}. 
The proposed VC scheme 
can accomplish over  96\% of what complete global
deduplication can do. In comparison, the SRB and sampled index~\cite{Dong2011,extreme_binning09,Guo2011}
can accomplish 97\% to 97.86\%.
\item {\em Low resource usage in deduplication}. 
The VC scheme achieves a 85K:1 ratio between raw snapshot data and memory usage
and is much more memory-efficient than 
SRB  with 4K:1 ratio and sampled index with 20K:1.
Both VC and SRB are designed for a distributed cluster architecture while
the sampled index method is for a single-machine architecture.
\item {\em Low cost in snapshot deletion}. 
\item {\em Higher availability}. 
The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block. The analysis shows that the replication degree
for the popular data set between 6 and 9 is good enough when the replication degree
for other data blocks is 3, and adds only a small cost to storage.
\end{itemize}
%Currently we are studying how the

>>>>

Our evaluation with an Alibaba dataset has the following results.
\begin{itemize}
\item {\em Competitive deduplication efficiency with a tradeoff}. 
The proposed VC scheme 
can accomplish over  96\% of what complete global
deduplication can do. In comparison, SRB~\cite{Dong2011,extreme_binning09}
can accomplish 97.86 while 
the sampled index~\cite{Guo2011} can deliver 97\% for a different test dataset. 
\item {\em Low resource usage in deduplication}. 
The VC scheme achieves a 85K:1 ratio between raw snapshot data and memory usage
and is much more memory-efficient than 
SRB  with 4K:1 ratio and sampled index with 20K:1.
Both VC and SRB are designed for a distributed cluster architecture while
the sampled index method is for a single-machine architecture.
\item {\em Low cost in snapshot deletion}. 
The VC deletion takes less than a minute for snapshot deletion 
\item {\em Higher availability}. 
The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block. The analysis shows that the replication degree
for the popular data set between 6 and 9 is good enough when the replication degree
for other data blocks is 3, and adds only a small cost to storage.
\end{itemize}
%Currently we are studying how the

### 2014-07-18 snapshot_system/paper_eval.tex
re

}
\begin{table}[htb]
\centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
&
     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
&
     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
&        &&     no-simi & \\ \hline
Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
Efficiency &          &       &           &      \\    \hline 
Memory &      46MB & 118MB  & 108MB & 2.4GB \\ 
per-machine &      &   &  &  \\ \hline
    \end{tabular}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

>>>>

}
\begin{table}[htb]
\centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
&
     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
&
     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
&        &&     no-simi & \\ \hline
Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
Efficiency &          &       &           &      \\    \hline 
Memory &      10MB & 118MB  & 108MB & 2.4GB \\ 
per-machine &      &   &  &  \\ \hline
    \end{tabular}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}
